On the relation of the entanglement spectrum to the bulk polarization \\ DRAFT

### 2021-02-03 version2/draft_mh.tex
added acknowledgement

\acknowledgments
{\em Acknowledgments.--} 
FUNDING
We thank Krishanu XX and Thors Hans Hansson for a critical reading of the manuscript.

>>>>

\acknowledgments
{\em Acknowledgments.--} 
The research in this grant was supported by the Swedish Research Council under grant no. 2017-05162 and the Knut and Alice Wallenberg foundation under grant no. 2017.0157. 
We thank Krishanu Roychowdhury and Thors Hans Hansson for helpful discussions and a critical reading of the manuscript.
